Thermodynamic response functions in a cell fluid model

### 2024-09-13 paper_text.tex
add width=column in includegraphics

>>>>

The equations of state~\eqref{eq:eosMT} and \eqref{eq:eosNT} are derived in the zero-mode approximation of the $\rho^4$-model, which imposes limits on their applicability. Specifically, in terms of density, the equations are  applicable for $\rho^*_{\rm min} \leq \rho^* < \rho^*_{\rm max}$, where $\rho^*_{\rm min}$ and $\rho^*_{\rm max}$ are determined by the parameters $\alpha^*$ and $p$. For parameters given in~\eqref{params}, these values were estimated in~\cite{KozlovskiiDobush2020} as $\rho^*_{\rm min} = 0.009$ and $\rho^*_{\rm max} = 1.946$.
